Personality and political beliefs across the lifespan

### 2019-12-08 scripts/manuscript.Rmd
Materials Section
Primary measures: TIPI and SECS

>>>>

**_Personality_** To assess participant personality traits, respondents completed the Ten Item Personality Inventory [@gosling2003very]. Participants were asked to indicate the extent to which they agreed or disagreed with statements describing themselves (e.g. “Extraverted, enthusiastic”; “Critical, quarrelsome”). Respondents rated each statement on a 7-point likert scale (1 = Strongly Disagree to 7 = Strongly Agree). Responses were coded such that higher values reflected greater identification with the personality trait .

**_Social and Economic Conservatism_** To assess participant levels of conservatism, respondents completed the 12-item Social and Economic Conservatism Scale [@everett201312]. Participants were asked to indicate the extent to which they feel positively or negatively about twelve distinct issues (eg. Abortion; Patriotism). Respondents rated each issue on a 100-point scale (0 indicates greater negativity and 100 indicates greater positivity). Responses were coded such that higher values reflected greater levels of conservatism.

### 2019-12-08 scripts/manuscript.tex
Materials Section
Primary measures: TIPI and SECS

@@

@@

>>>>

\textbf{\emph{Personality}} To assess participant personality traits, respondents completed the Ten Item Personality Inventory (Gosling, Rentfrow, \& Swann Jr, 2003). Participants were asked to indicate the extent to which they agreed or disagreed with statements describing themselves (e.g. \enquote{Extraverted, enthusiastic}; \enquote{Critical, quarrelsome}). Respondents rated each statement on a 7-point likert scale (1 = Strongly Disagree to 7 = Strongly Agree). Responses were coded such that higher values reflected greater identification with the personality trait .

\textbf{\emph{Social and Economic Conservatism}} To assess participant levels of conservatism, respondents completed the 12-item Social and Economic Conservatism Scale (Everett, 2013). Participants were asked to indicate the extent to which they feel positively or negatively about twelve distinct issues (eg. Abortion; Patriotism). Respondents rated each issue on a 100-point scale (0 indicates greater negativity and 100 indicates greater positivity). Responses were coded such that higher values reflected greater levels of conservatism.

@@

\leavevmode\hypertarget{ref-everett201312}{}%
Everett, J. A. (2013). The 12 item social and economic conservatism scale (secs). \emph{PloS One}, \emph{8}(12), e82131.

@@

\leavevmode\hypertarget{ref-gosling2003very}{}%
Gosling, S. D., Rentfrow, P. J., \& Swann Jr, W. B. (2003). A very brief measure of the big-five personality domains. \emph{Journal of Research in Personality}, \emph{37}(6), 504--528.
